Variational Monte Carlo on bosonic systems

### 2018-02-27 project_1/article/article.tex
Add explicit drift force for full system
Important typo in eq. 46, Green's function fraction

    \subsection{The drift force}
        A disadvantage in the use of the brute-force Metropolis algorithm is
        that we might be spending much computational resources in an
        uninteresting part of configuration space. To make smarter moves we will
        use the Metropolis-Hastings algorithm (which will be discussed in due
        time). This algorithm is dependent on the drift force of the system.
        \begin{align}
            \vf{F}(\vf{r})
            &=
            \frac{2\nabla\Psi_T(\vf{r})}{\Psi_T(\vf{r})}.
        \end{align}
        Using this expression we are able to move towards parts of
        configuration space where the gradient increases or decreases yielding a
        better choice of movements.

@@

Now we need to change the acceptance probability of the metropolis algorithm to something that takes
the new sampling method into account,
\begin{equation}
    q(x_{\text{new}}, x) = \frac{G(x, x_{\text{new}}, \Delta t)\abs{\psi_T(x_{\text{new}})}}{G(x_{\text{new}}, x, \Delta t)\abs{\psi_T(x)}}
\end{equation}
where $G$ is the Green's function to the Fokker-Planck equation,
\begin{align}
    G&(x_{\text{new}}, x, \Delta x) \nonumber \\
    &= \frac{1}{(4\pi D \Delta t)^{3N/2}}\exp\left(-\frac{(x_{\text{new}} - x - D\Delta t F(x))^2}{4D\Delta t} \right).
\end{align}

>>>>

@@

Now we need to change the acceptance probability of the metropolis algorithm to something that takes 
the new sampling method into account,
\begin{equation}
	q(x_{\text{new}}, x) = \frac{G(x, x_{\text{new}}, \Delta t)\abs{\psi_T(x_{\text{new}})}^2}{G(x_{\text{new}}, x, \Delta t)\abs{\psi_T(x)}^2}
\end{equation}
where $G$ is the Green's function to the Fokker-Planck equation,
\begin{align}
	G&(x_{\text{new}}, x, \Delta x) \nonumber \\
	&= \frac{1}{(4\pi D \Delta t)^{3N/2}}\exp\left(-\frac{(x_{\text{new}} - x - D\Delta t F(x))^2}{4D\Delta t} \right).
\end{align}
